Von Neumann-Morgenstern and Savage Theorems for Causal Decision Making

### 2020-08-30 Theory_and_decision/Draft/Theory_and_decision_draft.tex
cambios en applications

\subsection{Motivation}
Intelligent agents often face situations in which an action must be chosen in the presence of uncertain conditions; this means that an outcome will be observed according to some probability distribution given the action chosen by the agent. In many real-world applications, the agent doesn't have access to all of the parameters required to calculate the maximum utility, but if the agent knew that his actions and the possible consequences were \textit{causally related}, then she could attempt to discover this relations and \textit{use them} in order to predict consequences of actions better than if he only observes multiple action-outcome pairs as done in Reinforcement Learning \citep{sutton1998reinforcement}.

@@

\subsection{Main Result}
In this work we extend Pearl's result to the case where a decision maker \textit{does not know the causal mechanism} that controls her environment, so she holds \textit{beliefs} about possible causal models and uses such beliefs \textit{as if} they were true, as prescribed by \cite{joyce1999foundations}, in order to attempt to make a good choice given her beliefs. We provide an explicit way of choosing an optimal decision given what the decision maker believes about the causal structure of her environment, thus providing a causal version of Savage's Theorem. We take a normative point of view to study how causal relations should be used by a \textit{rational} agent when making decisions with uncertain consequences.

@@

In this work we use the Bayesian Game model in order to study what happens when several decision makers have certain knowledge about an environment which is controlled by some, unknown but fixed, causal mechanism. We study games in which the players actions \textit{cause} some consequence according to some unknown causal model. We apply our a rational choice criterion to formulate a Nash equilibrium for Causal Games by defining a probability updating for Bayesian Causal Games.

>>>>

\subsection{Motivation}
Intelligent agents often face situations in which an action must be chosen in the presence of uncertain conditions; this means that an outcome will be observed according to some probability distribution given the action chosen by the agent. In many real-world applications, the agent doesn't have access to all of the parameters, or even the distribution itself, required to calculate the maximum utility, but if the agent knew that his actions and the possible consequences were \textit{causally related}, then she could attempt to discover these relations and \textit{use them} in order to predict consequences of actions better than if he only observes multiple action-outcome pairs as done in Reinforcement Learning \citep{sutton1998reinforcement}.

@@

\subsection{Main Result}
In this work we extend Pearl's result to the case where a decision maker \textit{does not know the causal mechanism} that controls her environment, so she holds \textit{beliefs} about possible causal models and uses such beliefs \textit{as if} they were true, as prescribed by \cite{joyce1999foundations}, in order to attempt to make a good choice given her beliefs. We provide an explicit way of choosing an optimal decision given what the decision maker believes about the causal structure of her environment, thus providing a causal version of Savage's Theorem. We take a normative point of view to study how causal relations \textit{should} be used by a rational agent when making decisions which have uncertain consequences.

@@

In this work we use the Bayesian Game model in order to study what happens when several decision makers have certain knowledge about an environment which is controlled by some, unknown but fixed, causal mechanism in the form of a causal graphical model. In our model, the players actions' \textit{cause} some consequence according to the unknown causal model. We apply our rational choice criterion to formulate a Nash equilibrium for Causal Games.
